### 2015-03-05 FirstDraftMaterials/Draft.tex

% AR Model: Hugoniot Loci and Integral Curves
\subsection{Hugoniot Loci and Integral Curves}
The AR model starts from the system
\begin{align}
&\partial_t\rho + \partial_x(\rho v) = 0, \label{AW:eq1}\\
&\partial_t \left(v + p(\rho )\right) + v\partial_x \left( v + p(\rho )\right) = 0\label{AW:eq1.5}
\end{align}
with $p(\rho) = \rho^\gamma$.

@@

\subsubsection{Hugoniot Loci}
In order to consider the Hugoniot loci for this system we must first write the system in conversation form. 
To accomplish this, note that multiplying the first equation by $(v + p(\rho ))$ and the second equation 
by $\rho$ gives us the two equations 
\begin{align*}
&(v + p(\rho ))\partial_t\rho + (v + p(\rho ))\partial_x(\rho v) = 0,  \\
&\rho\partial_t \left(v + p(\rho )\right) + \rho v\partial_x \left( v + p(\rho )\right) = 0.
\end{align*}
Adding these two equations gives
\begin{align}\label{AW:eq2}
\partial_t \left(\rho\left(v + p(\rho )\right)\right) + \partial_x \left( \rho v\left(v + p(\rho )\right)\right) = 0.
\end{align}
Then from (\ref{AW:eq1}) and (\ref{AW:eq2}) we have the system 
\begin{align*}
&\partial_t\rho + \partial_x(\rho v) = 0, \\
&\partial_t \left(\rho\left(v + p(\rho )\right)\right) + \partial_x \left( \rho v\left(v + p(\rho )\right)\right) = 0.
\end{align*}
This can be rewritten as $q_t + f(q)_x = $ by defining
\begin{align*}
q = \left[ \begin{matrix}
\rho \\ y
\end{matrix}\right], \hspace{0.3in}
f(q) = \left[ \begin{matrix}
v\rho \\
vy
\end{matrix}\right].
\end{align*}
where $y = \rho\left(v + p(\rho )\right)$.
The Rankine-Hugoniot condition tells us that 
\begin{align*}
s(q_*- q) = f(q_*) - f(q).
\end{align*}
Therefore, from this condition we get the two equations
\begin{align}
s(\rho_* - \rho) = v_*\rho_* - v\rho, \label{AW:eq3}\\
s(y_* - y) = v_*y_* - vy.\label{AW:eq4}
\end{align}
With a little rearranging and by plugging in for $y$, these two equations can be rewritten as
\begin{align}
&\rho_*(s - v_*) = \rho (s - v), \label{AW:eq5}\\
&\rho_*(s - v_*)\left(v_* + p(\rho_* )\right) = \rho(s - v)\left(v + p(\rho )\right).\label{AW:eq6}
\end{align}
From (\ref{AW:eq5}), we know that there are two cases:

(a) $\rho_*(s - v_*) = \rho (s - v) = 0$. In this case we have that
\begin{align*}
s - v_* = s - v 
\end{align*}
except if one of the two densities, $\rho_*$, $\rho$ is zero. WHY DOES THIS NOT MATTER? Therefore, we can say that
\begin{align*}
v_* = v.
\end{align*}
Since the velocity does not change, this is a contact discontinuity. Using the fact that $v = v_*$ in (\ref{AW:eq4}) gives
\begin{align*}
y_*(s - v) = y(s - v).
\end{align*}
So, either $y = y_*$ or $s = v$. If $y = y_*$ we have a stationary point in the $Y = (\rho, y)$ plane, which does not 
describe a wave. Therefore, $s = v$. Note that we have no restrictions on $y$ other than its definition. 
Therefore this loci in the $Y$ plane is given by 
\begin{align*}
y = \rho ( v_* + p(\rho )).
\end{align*}
(b) $\rho_*(s - v_*) = \rho (s - v) \neq 0$. In this case, plugging this into (\ref{AW:eq6}) gives
\begin{align*}
\rho_*(s - v_*)\left(v_* + p(\rho_* )\right) &= \rho(s - v)\left(v + p(\rho )\right)\\
\rho(s - v)\left(v_* + p(\rho_* )\right) &= \rho(s - v)\left(v + p(\rho )\right)\\
v_* + p(\rho_* )&= v + p(\rho ).
\end{align*}
Therefore, the Hugoniot loci for this case in the Y plane are given by
\begin{align*}
y = v_* + p(\rho_* ),
\end{align*}
since $y = v + p(\rho )$ by definition. Note that solving (\ref{AW:eq3}) for $s$ gives
\begin{align*}
s = \frac{\rho_*v_* - \rho v}{\rho_* - \rho}.
\end{align*}
Using the fact that $v_* = v + p(\rho) - p(\rho_*)$, we get that
\begin{align*}
s = \frac{\rho_*\left( v + p(\rho) - p(\rho_*)\right)- \rho v}{\rho_* - \rho}
= v - \rho_*\frac{p(\rho ) - p(\rho_*)}{\rho - \rho_*}
\approx v - \rho p'(\rho)
\end{align*}
for $\rho_* \approx \rho$.

@@

\begin{figure}[h!]
 \centering
 \subfigure[$\lambda_1$-curves in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the U plane passing through
  the point $(\rho_*, v_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U.jpg}
   }
    \subfigure[$\lambda_1$-curves in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the M plane passing through 
 the point $(\rho_*,m_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M.jpg}
   }
       \subfigure[$\lambda_1$-curves in the Y plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the Y plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the Y plane passing through 
 the point $(\rho_*, y_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y.jpg}
   }
 \label{fig:AR_curves}
 \caption[Optional caption for list of figures]
 {Figures of the Hugonio loci and integral curves for $\lambda_1$ and $\lambda_2$ 
 in each of the different planes. Since the loci and integral curves coincide, they are 
 both simply called the ``curves'' in the captions of the above figures. 
 Figures (c), (f), (i) show both curves for a given point in each plane.}
\end{figure}

\subsubsection{Integral Curves}
In order to consider the integral curves for this system \cite{AwRascle2000} 
works from the system
\begin{align*}
&\partial_t \rho + \partial_x (\rho v) = 0 \\ 
&\partial_t v + \left(v - p'(\rho)\rho\right)\partial_x v = 0,
\end{align*}
where the second equation is found by multiplying (\ref{AW:eq1}) 
by $p'(\rho)$ and subtracting it from (\ref{AW:eq1.5}). 
This can be rewritten as $q_t + Aq_t = 0$ by defining
\begin{align*}
q = \left[ \begin{matrix}
\rho \\ v
\end{matrix}\right] , \hspace{0.3in}
A = \left[ \begin{matrix}
v & \rho \\
0 & v - p'(\rho ) \rho
\end{matrix}\right].
\end{align*}
The eigenvalues of $A$ are $\lambda_1 = v - p'(\rho ) \rho$ and 
$\lambda_2 = v$. Note that since $p(\rho ) = \rho^{\gamma}$ 
and $\rho \geq 0$, $\lambda_1 < \lambda_2$ so long as $\rho \neq 0$. 
Also note that if $\rho = 0$ then $A$ is no longer 
hyperbolic. The eigenvectors of $A$ are
\begin{align*}
r_1 = \left[ \begin{matrix}
1 \\ - p'(\rho )
\end{matrix}\right], \hspace{0.3in}
r_2 = \left[ \begin{matrix}
1 \\ 0
\end{matrix}\right].
\end{align*}
Using equation (13.24) from \cite{LeVeque2002} with $\alpha = 1$ tells us 
that the integral curves can be found by considering $q'(\xi ) = r_p$. 
For $p = 1$ this gives us the two equations
\begin{align*}
&\rho'(\xi ) = 1 \\
&v'(\xi ) = - p'(\rho ),
\end{align*}
which can be solved to find that we have parameratized our curve by $\rho$, 
and $v = - p'(\rho ) + c_1$ while $\rho$ is free, where $c_1$ is a constant. 
Since for a given point $(\rho_*, v_*)$ when $\rho = \rho_*$ we want 
$v = v_*$, we get that $c_1 = v_* + p'(\rho_*)$. Thus, the integral curve 
is given by 
\begin{align*}
v = v_* + p'(\rho_*) - p'(\rho ).
\end{align*}
This coincides with the Hugoniot loci from case (b). For $p = 2$, we get the 
two equations
\begin{align*}
&\rho'(\xi ) = 1 \\
&v'(\xi ) = 0,
\end{align*}
which can be solved to find that we have parameratized our curve by $\rho$, 
and that $v$ is a constant. Therefore, $v = v_*$ and $\rho$ is free. 
This coincides with the Hugoniot loci from case (a).

@@

\begin{figure}[h!]
 \centering
 \subfigure[$\lambda_1$-curves with contours of $\lambda_1$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U.jpg}
   }
    \subfigure[Valid waves for the point $q_l$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U_ql.jpg}
   }
    \subfigure[Valid waves for the point $q_r$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U_qr.jpg}
   }
    \subfigure[$\lambda_1$-curves with contours of $\lambda_1$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M.jpg}
   }
 \subfigure[Valid waves for the point $q_l$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M_ql.jpg}
   }
 \subfigure[Valid waves for the point $q_r$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M_qr.jpg}
   }
 \label{fig:AW_validity}
 \caption[Optional caption for list of figures]
 {Figures showing the calculation of the valid waves for a given point. Figures (a)
  and (d) show the $\lambda_1$ curves in black with the $\lambda_1$ contours 
  in magenta. The other figures show valid shocks in red and valid rarefaction 
  waves in green. The contact discontinuity is shown in blue.}
\end{figure}

Therefore, it is important to take into account the contour lines of $\lambda$ when 
looking at the loci and integral curves. Figures \ref{fig:AW_validity}(a) and 
\ref{fig:AW_validity}(d) show the $\lambda_1$-curves in the $U$ and $M$ planes,
with the contour lines of $\lambda_1$ shown in magenta. This information is used
to determine which areas of the $\lambda_1$ curves are valid shock waves and which
are valid rarefaction waves. The rest of the subfigures show the regions of validity for 
specific points $q_*$, depending on whether $q_* = q_l$ or $q_* = q_r$. For these plots,
$q_* = (\rho_*,v_*) = (0.2, 0.2)$. Note that the contact discontinuity is valid
anywhere in the plane.

% Examples
\section{Examples}
Brisa

>>>>

% AR Model: Hugoniot Loci and Integral Curves
\subsection{Hugoniot Loci and Integral Curves}
The AR model starts from the system
\begin{align}
&\partial_t\rho + \partial_x(\rho v) = 0, \label{AR:eq1}\\
&\partial_t \left(v + p(\rho )\right) + v\partial_x \left( v + p(\rho )\right) = 0\label{AR:eq1.5}
\end{align}
with $p(\rho) = \rho^\gamma$.

@@

\subsubsection{Hugoniot Loci}
In order to consider the Hugoniot loci for this system we must first write the system in conversation form. 
To accomplish this, note that multiplying the first equation by $(v + p(\rho ))$ and the second equation 
by $\rho$ gives us the two equations 
\begin{align*}
&(v + p(\rho ))\partial_t\rho + (v + p(\rho ))\partial_x(\rho v) = 0,  \\
&\rho\partial_t \left(v + p(\rho )\right) + \rho v\partial_x \left( v + p(\rho )\right) = 0.
\end{align*}
Adding these two equations gives
\begin{align}\label{AR:eq2}
\partial_t \left(\rho\left(v + p(\rho )\right)\right) + \partial_x \left( \rho v\left(v + p(\rho )\right)\right) = 0.
\end{align}
Then from (\ref{AR:eq1}) and (\ref{AR:eq2}) we have the system 
\begin{align*}
&\partial_t\rho + \partial_x(\rho v) = 0, \\
&\partial_t \left(\rho\left(v + p(\rho )\right)\right) + \partial_x \left( \rho v\left(v + p(\rho )\right)\right) = 0.
\end{align*}
This can be rewritten as $q_t + f(q)_x = $ by defining
\begin{align*}
q = \left[ \begin{matrix}
\rho \\ y
\end{matrix}\right], \hspace{0.3in}
f(q) = \left[ \begin{matrix}
v\rho \\
vy
\end{matrix}\right].
\end{align*}
where $y = \rho\left(v + p(\rho )\right)$.
The Rankine-Hugoniot condition tells us that 
\begin{align*}
s(q_*- q) = f(q_*) - f(q).
\end{align*}
Therefore, from this condition we get the two equations
\begin{align}
s(\rho_* - \rho) = v_*\rho_* - v\rho, \label{AR:eq3}\\
s(y_* - y) = v_*y_* - vy.\label{AR:eq4}
\end{align}
With a little rearranging and by plugging in for $y$, these two equations can be rewritten as
\begin{align}
&\rho_*(s - v_*) = \rho (s - v), \label{AR:eq5}\\
&\rho_*(s - v_*)\left(v_* + p(\rho_* )\right) = \rho(s - v)\left(v + p(\rho )\right).\label{AR:eq6}
\end{align}
From (\ref{AR:eq5}), we know that there are two cases:

(a) $\rho_*(s - v_*) = \rho (s - v) = 0$. In this case we have that
\begin{align*}
s - v_* = s - v 
\end{align*}
except if one of the two densities, $\rho_*$, $\rho$ is zero. WHY DOES THIS NOT MATTER? Therefore, we can say that
\begin{align*}
v_* = v.
\end{align*}
Since the velocity does not change, this is a contact discontinuity. Using the fact that $v = v_*$ in (\ref{AR:eq4}) gives
\begin{align*}
y_*(s - v) = y(s - v).
\end{align*}
So, either $y = y_*$ or $s = v$. If $y = y_*$ we have a stationary point in the $Y = (\rho, y)$ plane, which does not 
describe a wave. Therefore, $s = v$. Note that we have no restrictions on $y$ other than its definition. 
Therefore this loci in the $Y$ plane is given by 
\begin{align*}
y = \rho ( v_* + p(\rho )).
\end{align*}
(b) $\rho_*(s - v_*) = \rho (s - v) \neq 0$. In this case, plugging this into (\ref{AR:eq6}) gives
\begin{align*}
\rho_*(s - v_*)\left(v_* + p(\rho_* )\right) &= \rho(s - v)\left(v + p(\rho )\right)\\
\rho(s - v)\left(v_* + p(\rho_* )\right) &= \rho(s - v)\left(v + p(\rho )\right)\\
v_* + p(\rho_* )&= v + p(\rho ).
\end{align*}
Therefore, the Hugoniot loci for this case in the Y plane are given by
\begin{align*}
y = v_* + p(\rho_* ),
\end{align*}
since $y = v + p(\rho )$ by definition. Note that solving (\ref{AR:eq3}) for $s$ gives
\begin{align*}
s = \frac{\rho_*v_* - \rho v}{\rho_* - \rho}.
\end{align*}
Using the fact that $v_* = v + p(\rho) - p(\rho_*)$, we get that
\begin{align*}
s = \frac{\rho_*\left( v + p(\rho) - p(\rho_*)\right)- \rho v}{\rho_* - \rho}
= v - \rho_*\frac{p(\rho ) - p(\rho_*)}{\rho - \rho_*}
\approx v - \rho p'(\rho)
\end{align*}
for $\rho_* \approx \rho$.

@@

\begin{figure}[h!]
 \centering
 \subfigure[$\lambda_1$-curves in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the U plane passing through
  the point $(\rho_*, v_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U.jpg}
   }
    \subfigure[$\lambda_1$-curves in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the M plane passing through 
 the point $(\rho_*,m_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M.jpg}
   }
       \subfigure[$\lambda_1$-curves in the Y plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the Y plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the Y plane passing through 
 the point $(\rho_*, y_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y.jpg}
   }
 \caption[Optional caption for list of figures]
 {Figures of the Hugonio loci and integral curves for $\lambda_1$ and $\lambda_2$ 
 in each of the different planes. Since the loci and integral curves coincide, they are 
 both simply called the ``curves'' in the captions of the above figures. 
 Figures (c), (f), (i) show both curves for a given point in each plane.}
  \label{fig:AR_curves}
\end{figure}

\subsubsection{Integral Curves}
In order to consider the integral curves for this system \cite{AwRascle2000} 
works from the system
\begin{align*}
&\partial_t \rho + \partial_x (\rho v) = 0 \\ 
&\partial_t v + \left(v - p'(\rho)\rho\right)\partial_x v = 0,
\end{align*}
where the second equation is found by multiplying (\ref{AR:eq1}) 
by $p'(\rho)$ and subtracting it from (\ref{AR:eq1.5}). 
This can be rewritten as $q_t + Aq_t = 0$ by defining
\begin{align*}
q = \left[ \begin{matrix}
\rho \\ v
\end{matrix}\right] , \hspace{0.3in}
A = \left[ \begin{matrix}
v & \rho \\
0 & v - p'(\rho ) \rho
\end{matrix}\right].
\end{align*}
The eigenvalues of $A$ are $\lambda_1 = v - p'(\rho ) \rho$ and 
$\lambda_2 = v$. Note that since $p(\rho ) = \rho^{\gamma}$ 
and $\rho \geq 0$, $\lambda_1 < \lambda_2$ so long as $\rho \neq 0$. 
Also note that if $\rho = 0$ then $A$ is no longer 
hyperbolic. The eigenvectors of $A$ are
\begin{align*}
r_1 = \left[ \begin{matrix}
1 \\ - p'(\rho )
\end{matrix}\right], \hspace{0.3in}
r_2 = \left[ \begin{matrix}
1 \\ 0
\end{matrix}\right].
\end{align*}
Using equation (13.24) from \cite{LeVeque2002} with $\alpha = 1$ tells us 
that the integral curves can be found by considering $q'(\xi ) = r_p$. 
For $p = 1$ this gives us the two equations
\begin{align*}
&\rho'(\xi ) = 1 \\
&v'(\xi ) = - p'(\rho ),
\end{align*}
which can be solved to find that we have parameratized our curve by $\rho$, 
and $v = - p'(\rho ) + c_1$ while $\rho$ is free, where $c_1$ is a constant. 
Since for a given point $(\rho_*, v_*)$ when $\rho = \rho_*$ we want 
$v = v_*$, we get that $c_1 = v_* + p'(\rho_*)$. Thus, the integral curve 
is given by 
\begin{align*}
v = v_* + p'(\rho_*) - p'(\rho ).
\end{align*}
This coincides with the Hugoniot loci from case (b). For $p = 2$, we get the 
two equations
\begin{align*}
&\rho'(\xi ) = 1 \\
&v'(\xi ) = 0,
\end{align*}
which can be solved to find that we have parameratized our curve by $\rho$, 
and that $v$ is a constant. Therefore, $v = v_*$ and $\rho$ is free. 
This coincides with the Hugoniot loci from case (a).

@@

\begin{figure}[h!]
 \centering
 \subfigure[$\lambda_1$-curves with contours of $\lambda_1$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U.jpg}
   }
    \subfigure[Valid waves for the point $q_l$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U_ql.jpg}
   }
    \subfigure[Valid waves for the point $q_r$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U_qr.jpg}
   }
    \subfigure[$\lambda_1$-curves with contours of $\lambda_1$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M.jpg}
   }
 \subfigure[Valid waves for the point $q_l$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M_ql.jpg}
   }
 \subfigure[Valid waves for the point $q_r$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M_qr.jpg}
   }
 \caption[Optional caption for list of figures]
 {Figures showing the calculation of the valid waves for a given point. Figures (a)
  and (d) show the $\lambda_1$ curves in black with the $\lambda_1$ contours 
  in magenta. The other figures show valid shocks in red and valid rarefaction 
  waves in green. The contact discontinuity is shown in blue.}
   \label{fig:AR_validity}
\end{figure}

Therefore, it is important to take into account the contour lines of $\lambda$ when 
looking at the loci and integral curves. Figures \ref{fig:AR_validity}(a) and 
\ref{fig:AR_validity}(d) show the $\lambda_1$-curves in the $U$ and $M$ planes,
with the contour lines of $\lambda_1$ shown in magenta. This information is used
to determine which areas of the $\lambda_1$ curves are valid shock waves and which
are valid rarefaction waves. The rest of the subfigures show the regions of validity for 
specific points $q_*$, depending on whether $q_* = q_l$ or $q_* = q_r$. For these plots,
$q_* = (\rho_*,v_*) = (0.2, 0.2)$. Note that the contact discontinuity is valid
anywhere in the plane.

% Examples
\section{Examples}

\begin{figure}[h!]
 \centering
 \subfigure[Solution from the AR model.]{
  \includegraphics[width=70mm]{../MatlabCode/Images/AR_example1.jpg}
   }
% TODO: add subfigure for example1 in PW
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 1 from the AR and PW models.}
  \label{fig:example1}
\end{figure}

\begin{figure}[h!]
 \centering
 \subfigure[Solution from the AR model.]{
  \includegraphics[width=70mm]{../MatlabCode/Images/AR_example2.jpg}
   }
% TODO: add subfigure for example2 in PW
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 2 from the AR and PW models.}
  \label{fig:example2}
\end{figure}

\begin{table}[t]
\caption{Initial values used in examples 1 and 2.}
\begin{center}
\begin{tabular}{| c | c c |}
\hline
& Example 1 & Example 2\\
\hline
$v_l$ & 0.2 & 0 \\
$\rho_l$ & 0.3 & 0\\
$v_r$ & 0.3 & 0 .3\\
$\rho_r$ & 0.4 & 0.4\\
\hline
\end{tabular}
\end{center}
 \label{table:1}
\end{table}

Reproducing the Riemann problems found in \cite{AwRascle2000}, we consider two different examples. The variables used in these two examples are shown in Table \ref{table:1}. Note that in example 1, shown in Figure \ref{fig:example1}, the transition from $m_l = (\rho_l, v_l\rho_l)$ to $m_r = (\rho_r, v_r\rho_r)$ is first a shock and then a contact discontinuity. The middle state is denoted by $\tilde{m}$ in the figure. In example 2, show in Figure \ref{fig:example2}, the transition from $m_l = (\rho_l, v_l\rho_l)$ to $m_r = (\rho_r, v_r\rho_r)$ is a rarefaction wave, and there is no middle state.
